---
title: "book exercises"
output: html_document
---

Exercises - 5

###------
1. Fit a linear regression model to the `father.son` dataset with the father as the predictor and the son as the outcome. Give a p-value for the slope coefficient and perform the relevant hypothesis test. [Watch a video solution](https://www.youtube.com/watch?v=LxA2x2VvPWo&index=19&list=PLpl-gQkQivXji7JK1OP1qS7zalwUBPrX0).
```{r message=FALSE, warning=FALSE}
library(UsingR)
data(father.son)
model <- lm(sheight ~ fheight, data = father.son)
summary(model)$coef
```

The p-value almost 0 rejects the null hypothesis. It leads to accept the alternate hypothesis that average slope not 0. Ha <> 0

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)

g <- ggplot(data=father.son, aes(x=fheight, y=sheight)) +
  geom_point(size = 2, alpha=0.2) +
  geom_smooth(method="lm", color="red")
print(g)
```

###------
2. Refer to question 1. Interpret both parameters. Recenter for the intercept if necessary. [Watch a video solution](https://www.youtube.com/watch?v=YtXTK9ztE00&index=20&list=PLpl-gQkQivXji7JK1OP1qS7zalwUBPrX0).

A 0-height of the father doesn't make sense in using the intercept. Adjusting the intercept and center to the mean height of the father would be more meaningful.
```{r message=FALSE, warning=FALSE}
fheight.c <- father.son$fheight - mean(father.son$fheight)
new_dt <- data.frame(sheight=father.son$sheight,
                     fheight=fheight.c)
model2 <- lm(sheight~fheight, data=new_dt)
summary(model2)$coef
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2)
g <- ggplot(data=new_dt, aes(x=fheight, y=sheight)) +
  geom_point(size = 2, alpha=0.2) +
  geom_smooth(method="lm", color="red")
print(g)
```

```{r}
model3 <- lm(sheight ~ I(fheight-mean(fheight)),data=father.son)
summary(model3)$coef
```

###------
3. Refer to question 1. Predict the son’s height if the father’s height is 80 inches. Would you recommend this prediction? Why or why not? Watch a video solution.



###------
4. Load the mtcars dataset. Fit a linear regression with miles per gallon as the outcome and horsepower as the predictor. Interpret your coefficients, recenter for the intercept if necessary. Watch a video solution.

5. Refer to question 4. Overlay the fit onto a scatterplot. Watch a video solution.
Refer to question 4. Test the hypothesis of no linear relationship between horsepower and miles per gallon. Watch a video solution.

6. Refer to question 4. Predict the miles per gallon for a horsepower of 111. Watch a video solution.
