---
title: "Regression Model Project"
author: "Hashdevrunner"
output: html_document
---

##Executive Summary

##Data Exploration
Exploring the `mtcars` dataset with the most intuitive variables is the first step in achieving good analysis points. We prepare the variables in to categorical and continuous data.

```{r eval=FALSE}
data(mtcars); attach(mtcars)

#categorize the following variables Cylinder,Transmission
mtcars$cyl <- as.factor(cyl)
mtcars$am <- factor(am, labels = c("Automatic","Manual"))
mtcars$gear <- as.factor(gear)
mtcars$carb <- as.factor(carb)
mtcars$vs <- as.factor(vs) #what is this variable?
```

Exploring the mpg vs variables that can be intuitively guess resulted into identifiable patterns.
```{r echo=FALSE}
pairs(mpg ~ wt + disp + hp, 
      upper.panel = panel.smooth, data=mtcars)
```


The first intuitive variable we can explore is the MPG vs weight scatterplot.  There is a strong correlation that as the car gets heavier there is a decrease in mileage efficiency.

```{r echo=FALSE}
library(ggplot2)
#plot mpg vs wt
g1 <- ggplot(data = mtcars, aes(y = mpg, x = wt)) +
  ggtitle("mpg vs wt plot") +
  geom_point() + 
  geom_smooth(method = "lm") + 
  facet_grid(. ~ am, scales = "free")
print(g1)
```

Another strong relationship shown 

