---
title: "Regression Model Quiz 2"
author: "Hashdevrunner"
date: "Wednesday, April 08, 2015"
output: html_document
---



#####1. Consider the following data with x as the predictor and y as as the outcome.
```{r}
x <- c(0.61, 0.93, 0.83, 0.35, 0.54, 0.16, 0.91, 0.62, 0.62)
y <- c(0.67, 0.84, 0.6, 0.18, 0.85, 0.47, 1.1, 0.65, 0.36)
```
#####Give a P-value for the two sided hypothesis test of whether $\beta1$ from a linear regression model is 0 or not.

```{r}
fit <- lm(y~x, data.frame(x,y))
summary(fit)
summary(fit)$coefficients[2,4] #p-value of beta1
```

#####2. Consider the previous problem, give the estimate of the residual standard deviation
```{r}
summary(fit)$sigma
```

#####3. In the ```mtcars``` data set, fit a linear regression model of weight (predictor) on mpg (outcome). Get a 95% confidence interval for the expected mpg at the average weight. What is the lower endpoint?

```{r}
data(mtcars)
fit <- lm(mpg ~ I(wt-mean(wt)), mtcars)
sumCoef <- summary(fit)$coefficients
range <- sumCoef[1,1] + c(-1,1) * qt(.975, df = fit$df) * sumCoef[1,2]
range

library(ggplot2)
g <- ggplot(data=mtcars, aes(x = wt, y = mpg)) +
  geom_point(size = 2, alpha = 0.2, colour = "red") + 
  geom_smooth(method = "lm", colour = "blue")
print(g)

#alternate
newData <- c(mean(mtcars$wt))
range <- predict(fit, data.frame(wt=newData),interval="confidence")
range
```

#####4.Refer to the previous question. Read the help file for `mtcars`. What is the weight coefficient interpreted as?
The estimated expected change in mpg per 1000 lb increase in weight.

#####5. Consider again the `mtcars` data set and a linear regression model with mpg as predicted by weight (1,000 lbs). A new car is coming weighing 3000 pounds. Construct a 95% prediction interval for its mpg. What is the upper endpoint?
```{r}
newData <- c(3)
fit <- lm(mpg ~ wt, mtcars)

range <- predict(fit, data.frame(wt=newData), interval="prediction")
range
```

#####6. Consider again the `mtcars` data set and a linear regression model with mpg as predicted by weight (in 1,000 lbs). A “short” ton is defined as 2,000 lbs. Construct a 95% confidence interval for the expected change in mpg per 1 short ton increase in weight. Give the lower endpoint.

```{r}
fit <- lm(mpg ~ I(wt / 2), mtcars)
mean <- summary(fit)$coefficients[2,1]
se <- summary(fit)$coefficients[2,2]
df <- summary(fit)$df

#two sided T-test
range <- mean + c(-1,1) * qt(.975, df=df) * se
range
```

