---
title: "Regression Model Quiz 2"
author: "Hashdevrunner"
date: "Wednesday, April 08, 2015"
output: html_document
---



#####1. Consider the following data with x as the predictor and y as as the outcome.
```{r}
x <- c(0.61, 0.93, 0.83, 0.35, 0.54, 0.16, 0.91, 0.62, 0.62)
y <- c(0.67, 0.84, 0.6, 0.18, 0.85, 0.47, 1.1, 0.65, 0.36)
```
#####Give a P-value for the two sided hypothesis test of whether $\beta1$ from a linear regression model is 0 or not.

```{r}
fit <- lm(y~x, data.frame(x,y))
summary(fit)
summary(fit)$coefficients[2,4] #p-value of beta1
```

#####2. Consider the previous problem, give the estimate of the residual standard deviation
```{r}
summary(fit)$sigma
```

#####3. In the ```mtcars``` data set, fit a linear regression model of weight (predictor) on mpg (outcome). Get a 95% confidence interval for the expected mpg at the average weight. What is the lower endpoint?

```{r}
data(mtcars)
fit <- lm(mpg~wt, mtcars)
library(ggplot2)
g <- ggplot(mtcars, aes(x=wt, y=mpg)) +
  geom_point() +
  geom_abline(slope = coef(fit)["wt"],
              intercept = coef(fit)["(Intercept)"],
              color='BLUE') +
  stat_smooth(method = "lm", alpha = 0.2)
print(g)
```
