---
title: "Regression Model Quiz 1"
output: html_document
---

#####1. Give the value of $\mu$ that minimizes the least squares equation $\sum_{i=n}^n w(x{i}-\mu)$
```{r}
x <- c(0.18, -1.54, 0.42, 0.95)
w <- c(2, 1, 3, 1)
ans1 <- mean(rep(x,w))
print(paste("#1: ",ans1))
```


#####2. Fit the regression through the origin and get the slope treating y as the outcome and x as the regressor. (Hint, do not center the data since we want regression through the origin, not through the means of the data.)

```{r echo=FALSE}
library(ggplot2)
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
y <- c(1.39, 0.72, 1.55, 0.48, 1.19, -1.59, 1.23, -0.65, 1.49, 0.05)
df <- data.frame(x,y)
fit <- lm(y~x-1,data = df) #center at origin
fit2 <- lm(y~x,data = df)  #center to the data
# Do some plot here
g <- ggplot(data = data.frame(x,y), aes(x = x, y = y)) +
 geom_point() + 
 geom_abline(intercept = 0,slope=coef(fit)[1], color = 'Blue') +
 geom_abline(intercept = coef(fit2)[1], slope=coef(fit2)[2], color = 'Red') 
print(g)
```
```{r}
coef(fit)
```

#####3. Do data(mtcars) from the datasets package and fit the regression model with mpg as the outcome and weight as the predictor. Give the slope coefficient.

```{r echo = FALSE}
data(mtcars)
fit <- lm(mpg~wt, data = mtcars)
g <- ggplot( mtcars, aes(y = mpg, x = wt)) +
  geom_point() +
  geom_abline(intercept = coef(fit)["(Intercept)"], slope = coef(fit)["wt"], color = 'Blue')
print(g)
```
```{r}
coef(fit)
```

#####4. Consider data with an outcome (Y) and a predictor (X). The standard deviation of the predictor is one half that of the outcome. The correlation between the two variables is .5. What value would the slope coefficient for the regression model with Y as the outcome and X as the predictor?

```{r}
corr <- .5
sdY <- 1
sdX <- .5 * sdY
slope = corr * ( sdY / sdX) #beta1
print(slope)
```

#####5. Students were given two hard tests and scores were normalized to have empirical mean 0 and variance 1. The correlation between the scores on the two tests was 0.4. What would be the expected score on Quiz 2 for a student who had a normalized score of 1.5 on Quiz 1?

```{r}
corr = 0.4
z1 = 1.5
z2 = corr * z1
print(z2)
```

#####6. Consider the data given by the following```x <- c(8.58, 10.46, 9.01, 9.64, 8.86)```. What is the value of the first measurement if x were normalized (to have mean 0 and variance 1)?

```{r}
x <- c(8.58, 10.46, 9.01, 9.64, 8.86)
meanX <- mean(x)
sd <- sd(x)
z1 <- ( x - meanX ) / sd
print(z1[1])
```

#####7. Consider the following data set (used above as well). What is the intercept for fitting the model with x as the predictor and y as the outcome?
```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
y <- c(1.39, 0.72, 1.55, 0.48, 1.19, -1.59, 1.23, -0.65, 1.49, 0.05)
```

```{r}
df <- data.frame(x,y)
fit <- lm(y~x, df)
```
```{r echo=FALSE}
g <- ggplot(df, aes(y = y, x = x)) +
  geom_point() +
  geom_abline(intercept = coef(fit)["(Intercept)"], slope = coef(fit)["x"], color = 'Blue')
print(g)
print(coef(fit)[1]) #intercept
```

#####8. You know that both the predictor and response have mean 0. What can be said about the intercept when you fit a linear regression?
```{r}
x <- rnorm(20, mean = 0, sd = 1)
y <- rnorm(20, mean = 0, sd = 1)
df <- data.frame(x,y)
```
```{r echo=FALSE}
fit <- lm( y~x, df)
g <- ggplot(df, aes(y = y, x = x)) +
  geom_point() +
  geom_abline(intercept = coef(fit)["(Intercept)"], slope = coef(fit)["x"], color = 'Blue')
print(g)
```
```{r}
summary(fit)
```

#####9.Consider the data given by ```x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)```. What value minimizes the sum of the squared distances between these points and itself?

```{r}
x <- c(0.8, 0.47, 0.51, 0.73, 0.36, 0.58, 0.57, 0.85, 0.44, 0.42)
meanX <- mean(x)
print(meanX)
```
